\textbf{Selective DNA and Protein Isolation from Marine Macrophyte Surfaces}

### 2021-03-25 submission/manuscript.tex

An aliquot of isolated DNA was treated with RNase A (final concentration
200 \si{\ug\per\ml}) for 2 \si{\hour} at 37 \si{\degreeCelsius}. The DNA
concentration was determined using the Quant-iT PicoGreen dsDNA Assay
Kit (Invitrogen, USA) according to the manufacturer's instructions and
diluted to 1 \si{\ng\per\ul}. The V4 region of the 16S rRNA gene was
amplified using a two-step PCR procedure. In the first PCR the 515F
(\(5'\)-GTGYCAGCMGCCGCGGTAA-\(3'\)) and 806R
(\(5'\)-GGACTACNVGGGTWTCTAAT-\(3'\)) primers from the Earth Microbiome
Project (\url{https://earthmicrobiome.org/protocols-and-standards/16s/})
were used to amplify the target region (Caporaso et al., 2012; Apprill
et al., 2015; Parada et al., 2016). These primers contained on their
\(5'\) end a tagged sequence. Each sample was amplified in four parallel
25 \si{\ul} reactions of which each contained 1 × Q5 Reaction Buffer,
0.2 \si{\milli\Molar} dNTPmix, 0.7 \si{\mg\per\ml} BSA (Bovine Serum
Albumin), 0.2 \si{\micro\Molar} of forward and reverse primers, 0.5 U of
Q5 High-Fidelity DNA Polymerase (New England Biolabs, USA) and 5
\si{\ng} of DNA template. Cycling conditions were: initial denaturation
at 94 \si{\degreeCelsius} for 3 \si{\minute}, 20 cycles of denaturation
at 94 \si{\degreeCelsius} for 45 \si{\s}, annealing at 50
\si{\degreeCelsius} for 60 \si{\s} and elongation at 72
\si{\degreeCelsius} for 90 \si{\s}, finalized by an elongation step at
72 \si{\degreeCelsius} for 10 \si{\minute}. The four parallel reactions
volumes were pooled and PCR products were purified using the GeneJET PCR
Purification Kit (Thermo Fisher Scientific, USA) according to the
manufacturer's instructions and following the protocol that included
isopropanol addition for better small DNA fragment yield. The column was
eluted in 30 \si{\ul} of deionized water. Purified PCR products were
sent for Illumina MiSeq sequencing (2 × 250 bp) at IMGM Laboratories,
Martinsried, Germany. Before sequencing at IMGM, the second PCR
amplification of the two-step PCR procedure was performed using primers
targeting the tagged region incorporated in the first PCR. In addition,
these primers contained adapter and sample-specific index sequences. The
second PCR was carried out for 8 cycles. Beside samples, a positive and
negative control were sequenced. A negative control was comprised of
four parallel PCR reactions without DNA template, while for a positive
control a mock community composed of evenly mixed DNA material
originating from 20 bacterial strains (ATCC MSA-1002, ATCC, USA) was
used. Partial 16S rRNA sequences obtained in this study have been
deposited in the European Nucleotide Archive (ENA) at EMBL-EBI under
accession numbers SAMEA6786270, SAMEA6648792 -- SAMEA6648794,
SAMEA6648809 -- SAMEA6648811 and SAMEA6648824.

>>>>

An aliquot of isolated DNA was treated with RNase A (final concentration
200 \si{\ug\per\ml}) for 2 \si{\hour} at 37 \si{\degreeCelsius}. The DNA
concentration was determined using the Quant-iT PicoGreen dsDNA Assay
Kit (Invitrogen, USA) according to the manufacturer's instructions and
diluted to 1 \si{\ng\per\ul}. The V4 region of the 16S rRNA gene was
amplified using a two-step PCR procedure. In the first PCR the 515F
(\(5'\)-GTGYCAGCMGCCGCGGTAA-\(3'\)) and 806R
(\(5'\)-GGACTACNVGGGTWTCTAAT-\(3'\)) primers from the Earth Microbiome
Project (\url{https://earthmicrobiome.org/protocols-and-standards/16s/})
were used to amplify the target region (Caporaso et al., 2012; Apprill
et al., 2015; Parada et al., 2016). These primers contained on their
\(5'\) end a tagged sequence. Each sample was amplified in four parallel
25 \si{\ul} reactions of which each contained 1 × Q5 Reaction Buffer,
0.2 \si{\milli\Molar} dNTPmix, 0.7 \si{\mg\per\ml} BSA (Bovine Serum
Albumin), 0.2 \si{\micro\Molar} forward and reverse primers, 0.5 U of Q5
High-Fidelity DNA Polymerase (New England Biolabs, USA) and 5 \si{\ng}
of DNA template. Cycling conditions were: initial denaturation at 94
\si{\degreeCelsius} for 3 \si{\minute}, 20 cycles of denaturation at 94
\si{\degreeCelsius} for 45 \si{\s}, annealing at 50 \si{\degreeCelsius}
for 60 \si{\s} and elongation at 72 \si{\degreeCelsius} for 90 \si{\s},
finalized by an elongation step at 72 \si{\degreeCelsius} for 10
\si{\minute}. The four parallel reactions volumes were pooled and PCR
products were purified using the GeneJET PCR Purification Kit (Thermo
Fisher Scientific, USA) according to the manufacturer's instructions and
following the protocol that included isopropanol addition for better
small DNA fragment yield. The column was eluted in 30 \si{\ul} of
deionized water. Purified PCR products were sent for Illumina MiSeq
sequencing (2 × 250 bp) at IMGM Laboratories, Martinsried, Germany.
Before sequencing at IMGM, the second PCR amplification of the two-step
PCR procedure was performed using primers targeting the tagged region
incorporated in the first PCR. In addition, these primers contained
adapter and sample-specific index sequences. The second PCR was carried
out for 8 cycles. Beside samples, a positive and negative control were
sequenced. A negative control was comprised of four parallel PCR
reactions without DNA template, while for a positive control a mock
community composed of evenly mixed DNA material originating from 20
bacterial strains (ATCC MSA-1002, ATCC, USA) was used. Partial 16S rRNA
sequences obtained in this study have been deposited in the European
Nucleotide Archive (ENA) at EMBL-EBI under accession numbers
SAMEA6786270, SAMEA6648792 -- SAMEA6648794, SAMEA6648809 -- SAMEA6648811
and SAMEA6648824.
